### 2021-02-25 poster/poster.tex
Adding poster.

%%%% Better Poster latex template example v1.0 (2019/04/04)
%%%% GNU General Public License v3.0
%%%% Rafael Bailo
%%%% https://github.com/rafaelbailo/betterposter-latex-template
%%%% 
%%%% Original design from Mike Morrison
%%%% https://twitter.com/mikemorrison

\documentclass[a0paper,fleqn]{betterposter}

%% Set up color palettes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Color palette GreenOrange_6 from
% https://jiffyclub.github.io/palettable/tableau/
\definecolor{pgreen}     {RGB}{50,162,81}
\definecolor{porange}    {RGB}{255,127,15}
\definecolor{pblue}      {RGB}{60,183,204}
\definecolor{pyellow}    {RGB}{255,217,74}
\definecolor{pteal}      {RGB}{57,115,124}
\definecolor{pauburn}    {RGB}{184,90,13}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{mygray}{gray}{0.9}

\usepackage{hyperref}
\hypersetup{pdfborder={0 0 0},
            colorlinks=true,
            % colorlinks=false,
            urlcolor=porange,
            linkcolor=pauburn,
            citecolor=pteal}

\input{../utils/notation.tex}

\usepackage[backend=biber,style=numeric]{biblatex}
\addbibresource{../bib/references.bib}

%%%% Uncomment the following commands to customise the format

%% Setting the width of columns
% Left column
\setlength{\leftbarwidth}{0.28\paperwidth}
% Right column
\setlength{\rightbarwidth}{0.28\paperwidth}

%% Setting the column margins
% Horizontal margin
\setlength{\columnmarginvertical}{0.02\paperheight}
% Vertical margin
\setlength{\columnmarginhorizontal}{0.02\paperheight}
% Horizontal margin for the main column
\setlength{\maincolumnmarginvertical}{0.02\paperheight}
% Vertical margin for the main column
\setlength{\maincolumnmarginhorizontal}{0.02\paperheight}

%% Changing font sizes
% Text font
%\renewcommand{\fontsizestandard}{\fontsize{28}{35} \selectfont}
% Main column font
%\renewcommand{\fontsizemain}{\fontsize{28}{35} \selectfont}
% Title font
%\renewcommand{\fontsizetitle}{\fontsize{28}{35} \selectfont}
% Author font
%\renewcommand{\fontsizeauthor}{\fontsize{28}{35} \selectfont}
% Section font
%\renewcommand{\fontsizesection}{\fontsize{28}{35} \selectfont}

%% Changing font sizes for a specific text segment
% Place the text inside brackets:
% {\fontsize{28}{35} \selectfont Your text goes here}

%% Changing colours
% Background of side columns
%\renewcommand{\columnbackgroundcolor}{black}
% Font of side columns
%\renewcommand{\columnfontcolor}{gray}
% Background of main column
%\renewcommand{\maincolumnbackgroundcolor}{empirical}
%\renewcommand{\maincolumnbackgroundcolor}{theory}
%\renewcommand{\maincolumnbackgroundcolor}{methods}
%\renewcommand{\maincolumnbackgroundcolor}{intervention}
% Font of main column
%\renewcommand{\maincolumnfontcolor}{gray}

\begin{document}
\betterposter{
%%%%%%%% MAIN COLUMN

\maincolumn{
%%%% Main space

\vspace{-2.5ex}
{\raggedright
All three models perform well, PYP model performs slightly better.}

\vspace{-1.5ex}
\begin{center}
\fcolorbox{white}{white}{
\begin{minipage}[t]{0.92\textwidth}
\begin{center}
\vspace{-1.5ex}
\includegraphics[width=0.92\textwidth]{../images/from-project-repo/poster-nchars-model-distance-violin-cropped.pdf}\\
\vspace{-3.3ex}
\includegraphics[width=0.92\textwidth]{../images/from-project-repo/poster-nchars-nevents-cropped.pdf}\\
\vspace{-2.5ex}
\includegraphics[width=0.92\textwidth]{../images/from-project-repo/poster-match-nevents-cropped-rasterized.pdf}
\vspace{-1.5ex}
\end{center}
\end{minipage}}
\end{center}

\vspace{-20ex}
}{
%%%% Bottom space

%% QR code
\hspace{10em}
\qrcode{../images/qr-code.png}{../images/smart-phone-white.png}{
\textbf{Take a picture} to visit
\\the \textbf{project website}
}
% \compactqrcode{../images/qr-code.png}{
% \textbf{Take a picture} to
% \\visit the project website
% }
% Smartphone icon
% Author: Freepik
% Retrieved from: https://www.flaticon.com/free-icon/smartphone_65680

%% Compact QR code (comment the previous command and uncomment this one to switch)
%\compactqrcode{img/qrcode}{
%\textbf{Take a picture} to
%\\download the full paper
%}

}

}{
%%%%%%%% LEFT COLUMN

\title{Improving estimation of shared evolutionary events}
\author{Tashitso Anamza}
\author{Jamie Oaks}
\vspace{0.5ex}
\institution{Auburn Univeristy}

\vspace{-2ex}
\section{Background}
\vspace{-0.5ex}
Environmental processes that cause speciation across communities of species
should generate patterns of divergences that are temporally clustered across
species.
\href{http://phyletica.org/ecoevolity/}{Ecoevolity}
is a tool for testing such patterns by estimating shared divergence
times among pairs of populations using genomic data and Bayesian model choice
\cite{Oaks2018ecoevolity}.

\vspace{0.5ex}
\begin{center}
\begin{minipage}[t]{0.6\linewidth}
\includegraphics[width=0.9\linewidth]{../images/from-ecoevolity-tikz-repo/div-model-311-labels.pdf}\\
{\fontsize{28}{35} \selectfont %
An example of a shared divergence between 2 of 3 pairs of lizard populations.}
\end{minipage}
\end{center}

\vspace{1.5ex}
The number of ways the population pairs can share divergence times (i.e., the
number of divergence models) gets large as the number of species being compared
increases\cite{Bell1934}, so \textbf{we need flexible and efficient ways of assigning
    probabilities to all of them}.

\vspace{1.5ex}
\textbf{We implemented and compared 3 ways to assign prior probabilities to divergence
models}:
\vspace{1ex}
\begin{description}
    \item[Dirichlet process (DP)---] Commonly used in Bayesian statistics
        for clustering random variables. The process is controlled by a
        concentration parameter \cite{Ferguson1973, Antoniak1974}.
    \item[Pitman-Yor process (PYP)---] A generalization of the DP.  It adds
        a discount parameter that provides flexibility over the tail behavior
        of the process \cite{PitmanYor1997}.
    \item[Uniform prior---] In its simplest form, all divergence models are
        equally probable. However, we added a ``split-weight'' parameter to
        favor more or fewer divergence times; the prior probabilities of models
        with the same number of divergence times are always equal.
\end{description}

%% This fills the space between the content and the logo
\vfill

%% Institution logo
% \begin{center}
% \includegraphics[height=16ex]{../images/auburn-phylo-mtan-2014-orange.pdf}\\
% \end{center}

}{
%%%%%%%% RIGHT COLUMN

\vspace{-4ex}
\section{Methods}
To compare the \textbf{DP}, \textbf{PYP}, and \textbf{uniform} priors on
divergence models, we:
\begin{itemize}
\item Simulated 720 datasets of 500k biallelic characters from 10 pairs of
    populations under the \textbf{DP}, \textbf{PYP}, and \textbf{uniform}
    priors.
\item Simulated 720 datasets of 5k, 50k, and 500k characters under a model
    where the 10 pairs of populations all \textbf{diverge independently};
    their divergence times are drawn from an exponential distribution with a
    mean of 0.05 subsitutions per site.
    \textbf{This is the most challenging divergence model to estimate}.
\item Analyzed each of these datasets, with and without invariant characters,
    under the \textbf{DP}, \textbf{PYP}, and \textbf{uniform} priors
    to determine which is best at estimating the correct number of divergence
    times and assignment of pairs to those times.
\end{itemize}

\vspace{-1ex}
\section{Conclusions}
All three priors on divergence models performed well.
The \textbf{PYP prior performed slightly better than the DP and uniform
    priors},
likely due to the additional flexibility provided by the discount parameter.
\textbf{All three priors performed much better when invariant characters were
included in analyses.}

\vspace{-1ex}
\section{Acknowlegdements}
We thank all the members of the
\href{http://phyletica.org}{Phyletica Lab},
and NSF for funding this work (DEB 1656004).
% The computational work was made possible by the Auburn University (AU) Hopper
% Cluster supported by the AU Office of Information Technology.
This poster is based on the
\href{https://github.com/rafaelbailo/betterposter-latex-template}{Better Poster Latex Template}
developed by
\href{https://github.com/rafaelbailo}{Rafael Bailo}

\AtNextBibliography{\Huge}
\vspace{-1ex}
\section{References}
\printbibliography[heading=none]

\vfill

\begin{center}
\includegraphics[height=16ex]{../images/auburn-phylo-mtan-2014-orange.pdf}
\hspace{2em}
\includegraphics[height=16ex]{../images/aumnh-crop.png}
\end{center}

}
\end{document}

### 2021-02-25 manuscript/ms.tex
Working on the model description.

%&<latex>
\documentclass[letterpaper,12pt]{article}
\pdfoutput=1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../utils/preamble.tex}
\input{../utils/environments.tex}
\input{../utils/macros.tex}
\input{../utils/notation.tex}

\newcommand{\ifdoublespacing}[2]{#1}
% \newcommand{\ifdoublespacing}[2]{#2}
\newcommand{\iflinenumbers}[2]{#1}
% \newcommand{\iflinenumbers}[2]{#2}
% \newcommand{\ifragged}[2]{#1}
\newcommand{\ifragged}[2]{#2}

\usepackage[round]{natbib}
\usepackage{amsmath}
\title{A Pitman-Yor process prior for estimating shared evolutionary events}
% \title{Comparing hiearchicial Bayesian priors for estimating shared evolutionary events}

\author[1]{Tashitso Anamza}
\author[1]{Jamie R.\ Oaks \thanks{Corresponding author: \href{mailto:joaks@auburn.edu}{\tt joaks@auburn.edu}}}
\affil[1]{Department of Biological Sciences \& Museum of Natural History, Auburn University, Auburn, Alabama 36849}

\date{\today}

\makeatletter
\let\msTitle\@title
\let\msAuthor\@author
\let\msDate\@date
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\ifragged{
\raggedright
}{}

\iflinenumbers{
\begin{linenumbers}
}{}

\textbf{Running head}: \uppercase{Estimating shared evolutionary events}

{\let\newpage\relax\maketitle}

\newpage

\ifdoublespacing{
\doublespacing
}{}

\begin{abstract}
    Abstract here \ldots

    \vspace{6pt}
    \noindent\textbf{KEY WORDS:}
\end{abstract}

\newpage

\section{Introduction}

In this study, we compared the performance of 3 models (Dirichlet prior, Pitman-Yor prior and Uniform prior) 
that are implemented in Ecoevolity software which is the primary software we used to estimate the number of shared divergence time 
among 10 pairs of populations in the past. We simulated data and know the true number of divergence time from it. We are interested 
to estimate the number of divergence time from the generated data. We generated data under 5 various ways to putting prior over all
of the ways that we can assign a pair to divergence event. And then we analyzed the data under 3 models that we can model  
and have some sense of comparison. We are interested in how well the models have estimated the divergence time and how well 
the models have estimated what population pairs belong to which divergence time.

Before going further we needed to assign prior probabilities to 3 models; how probable each model is. Dirichlet-process prior 
assigns prior to a new category with probability of \[\frac{1}{a+1}\] and an exsiting category with probability of \[\frac{a}{a+1}\]. The concentration parameter(a) 
makes the DP flexible because we can adjust the concentration parameter to fit our prior expectation. We can put a distribution on the 
concetration parameter and integrate over uncertainty about the prior probabilities of the divergence models. Pitman-Yor process prior is 
generalization of Dirichlet process. There is a discount parameter(d) added in PYP and when d=0 PYP converges to DP. Dirichlet has an exponential tail 
and the discount parameter gives the PYP flexibity over the tail behavior. Uniform prior is every possible divergence model is equally probable. 
Then we have specified the priors in the config files for each of these 3 models that they are comparable to each other to assess the behavior of the models.

We used these 3 config files and then added 2 more configs (independent and simutanous configs ) to simulate datasets. Independent config 
basically spefifies there are 10 divergence times and each population diverged independently. Simutanous config specifies that the populations 
diverged simutanously and there is 1 shared event. And there is another config file which ignores the constant sites(characters). A total of 6 config 
files are specified to simulate the datasets. We used these 6 config files 4 times to generate scripts and then simulated 10 datasets under each of 
these 5 models with 5000,000 characters. Then we analyzed the data under 3 models and the results show that Pitman-Yor process is doing better job handling 
most difficult scenario all 10 pairs diverging independetly because PYP is more flexible model. The coverage is more robust for Pitman-Yor process twice likely.
So we are interested to see whether this pattern holds with less data. We decided to do another simulation with 4 varying datasets 5,000, 10,000, 50,000, and 100,000. 
All the datasets simulated under 5 models and then analyzed these datasets under 3 models (DP, PYP, and SW). There are equal number of replicates for both simulations 
a total of 720 replicates for each simulation. We found that with varying datasets suggest the same Pitman-Yor process has 2 parameters and more flexible might 
have some advantages especially when it is wrong.

\section{Model}

Here we provide a summary of the model implemented in \ecoevolity; please see
\citet{Oaks2018ecoevolity} and \citet{Oaks2019codemog} for a full description.
Our model allows for an arbitrary number of two types of temporal comparisons:
\begin{enumerate}
    \item A population that experienced a change from effective population size
        \epopsize[\rootpopindex]
        to effective size
        \epopsize[\descendantpopindex{}]
        at time \comparisonetime in the past.
        We will refer to this as a \emph{demographic comparison},
        and refer to the population before and after the change in population
        size as ``ancestral'' and ``descendant'', respectively.
    \item A population that diverged at time \comparisonetime in the past into
        two descendant populations, each with unique effective population
        sizes.
        We will refer to this as a \emph{divergence comparison}.
\end{enumerate}
For simplicity, we will use terminology related to divergence comparions, but
all of the theory discussed below also applies to demographic comparisons.

For each comparison, we assume we have sampled unlinked biallelic characters;
i.e., each character evolved along a gene tree that is independent of the
other characters, conditional on the population history.
We assume these characters evolved along their gene trees according to a
finite-sites continuous-time Markov chain model (CTMC).
The equilibrium frequency (\gfreq) of the two character states can be
estimated, making the CTMC model a two-state, general, time-reversible model
\citep{Tavare1986}.
Alternatively, if the state frequencies are constrained to be equal, the CTMC
model is a two-state analog of the ``JC69'' model of nucleotide substitution
\citep{JC1969}.
For the divergence times to be comparable among comparisons, the relative or
absolute mutation rate (\murate) or each pair must be specified or given an
informative prior probability distribution.
\citep{Oaks2018ecoevolity,Oaks2019codemog}.

The primary goal is to infer the temporal clustering of divergences across
\ncomparisons comparisons.
At one extreme, all \ncomparisons could have diverged at the same time,
and at the other extreme, all \ncomparisons diverged independently.
This presents a model-choice problem, where the number of possible models
is the number of ways we can assign \ncomparisons comparisons to
$1, 2,  \ldots, \ncomparisons$ divergence times
\citep[the Bell number;][]{Bell1934}.
Below, we use \etimesets to represent the partitioning of comparisons to
divergence events, which we will also refer to as a ``divergence model,'' and
\etimes to represent the unique divergence times within \etimesets.

We use a full-likelihood Bayesian approach to jointly infer
the divergence model (\etimesets), divergence times
(\etimes),
and comparison-specific parameters (\epopsize, \murate, and \gfreq)
\citep{Oaks2018ecoevolity,Oaks2019codemog}.
We compare three models for specifying the probability of all
possible divergence models (\etimesets):
A Dirichlet-process (DP), Pitman-Yor process (PYP), and
weighted-uniform (WU) model.
For all of these models we assume the time of each divergence event (\etime) is
distributed according to a parametric continuous probability distribution, like
a gamma.

\subsection{Dirichlet-process (DP) model}

\begin{linenomath}
\citet{Oaks2018ecoevolity} treated the number of divergence events and the
assignment of comparisons to those events as random variables under a Dirichlet
process \citep{Ferguson1973, Antoniak1974}.
The concentration parameter, \concentration, controls how clustered the
Dirichlet process is, and determines the probability of all possible \etimesets
(i.e., all possible set partitions of \ncomparisons comparisons).
To get these probabilities, we can assign comparisons to divergence events one
at a time, following a simple rule.
When assigning the $i^{th}$ comparison, we assign it to its own event
(i.e., a new divergence event with a unique time) with probability
\begin{equation}
    \frac{\concentration}{\concentration + i - 1},
    \label{eq:dpnewcat}
\end{equation}
or we assign it to an existing event $x$ with probability
\begin{equation}
    \frac{n_x}{\concentration + i - 1}.
    \label{eq:dpexistingcat}
\end{equation}
where $n_x$ is the number of comparisons already assigned to event $x$.
\end{linenomath}

\subsection{Pitman-Yor-process (PYP) model}

\begin{linenomath}
\citet{PitmanYor1997} generalized the Dirichlet process by adding a
``discount'' parameter (\discount) that can take values from 0--1.
% The rule governing the PYP is very similar to the DP.
When assigning the $i^{th}$ comparison, we assign it to its own event
with probability
\begin{equation}
    \frac{\concentration + \nexistingcats \discount}{\concentration + i - 1},
    \label{eq:pypnewcat}
\end{equation}
where \nexistingcats is the number of events that currently exist (i.e., that have at
least one comparison assigned to it).
Alternatively, we assign it to an existing event $x$ with probability
\begin{equation}
    \frac{n_x - \discount}{\concentration + i -1}.
    \label{eq:pypexistingcat}
\end{equation}
Notice, when $\discount = 0$, the PYP is equivalent to the DP.
\end{linenomath}

\subsection{Weighted-uniform (\wunif) model}
We have also implemented a uniform prior over divergence models, where we can
assume \emph{a priori} that every possible divergence model (\etimesets) is
equally probable.
Furthermore, we added a ``split weight'' parameter, which we denote as
\splitweight, to provide flexibility for the prior probabilities of
models with different numbers of events.
For a given model with \nevents divergence events, the relative probability
of each model with $\nevents + 1$ events is \splitweight,
and the relative probability of each model with $\nevents - 1$ events is
$\frac{1}{\splitweight}$.
More generally, the relative probability of each model with
$\nevents + n$
events is
$\splitweight{}^n$,
and the relative probability of each model with
$\nevents - n$
events is
$\frac{1}{\splitweight{}^n}$.
When $\splitweight = 1$, all divergence models are equally probable.

\subsection{Approximating the posterior with MCMC}

We use Markov chain Monte Carlo (MCMC) algorithms to sample from the joint
posterior distribution of the divergence model (\etimesets), divergence times
(\etimes), effective population sizes (\epopsize), and any mutation rate
(\murate) or substitution parameters (\gfreq) that are free to vary
\citep{Oaks2018ecoevolity,Oaks2019codemog}.
We use a suite of univariate and multivariate Metropolis-Hastings moves to
update the parameters of the model \citep{Metropolis1953,Hastings1970}.
The latter improve mixing in the face of correlations among divergence times,
population sizes, and mutation rates \citep[see][]{Oaks2018ecoevolity}.

Because \etimesets can differ in the number of divergence-time parameters, we
also need to use trans-dimensional MCMC algorithms to sample over all possible
divergence models.
Under the PYP, and the special case of the DP, the order of the comparisons
does not affect the probability of the model.
In other words, divergence models (\etimesets) that share the same integer
partition (i.e., the same number of events with the same number of comparisons
assigned to them) are equally probable.
Hence, the comparisons are exchangeable under the PYP and DP priors.
This allows us to use the Gibbs sampling algorithm (Algorithm 8) of
\citet{Neal2000} to update the \etimesets during the MCMC chain.

Unlike the PYP and DP, where divergence events with the same
integer partition were equally probably, under the
\wunif prior, divergence events that share the same number of events (\nevents) are
equally probable.
This means that the comparisons are not exchangeable under the \wunif prior,
and thus Gibbs sampling will not work to sample \etimesets under the \wunif
prior.
Instead we use reversible-jump MCMC moves under the \wunif prior.

\subsubsection{reversible-jump MCMC}
Layout the rjMCMC moves here \ldots

\subsection{Software implementation and project documentation}

The models outlined above are implemented in the open-source \cpp package,
\ecoevolity, which is freely available from
\url{https://github.com/phyletica/ecoevolity}, with documentation available
at
\url{http://phyletica.org/ecoevolity/}.
The test suite of \ecoevolity
validates the likelihood calculations and that the MCMC algorithms sample from
the expected prior distribution when data are ignored.
All of our analyses were performed with
Commit c1685dfa
of the \ecoevolity software package,
and all of the functionality included in this commit is part of
the release of Version \highLight{X.X.X}.
A detailed history of this project, including all of the scripts
needed to produce our results, is available at
\url{https://github.com/phyletica/ecoevolity-model-prior}
(\highLight{Cite Zenodo archive of repo here}).
% \citep{Anamza2020zenodo}.
The project repository includes detailed documentation and tutorials of our
work, which is hosted as a website at
\url{http://phyletica.org/ecoevolity-model-prior/}.

\section{Methods}

\subsection{Analyses of simulated data}

We used \simcoevolity and \ecoevolity of the \ecoevolity software
package
\citep[Version 0.3.2 Commit c1685dfa][]{Oaks2018ecoevolity}
to simulate and analyze \datasets, respectively.
Each simulated \dataset comprised biallelic characters from 2 diploid
individuals (4 genomes) sampled per population from 10 pairs of populations
(i.e., 10 divergence comparisons).
We assumed the mutation rates were equal and 1 across the 10 pairs of
populations, such that time and effective population sizes are scaled by the
mutation rate.
The times of divergence events were exponentially distributed with a mean 0.05
expected subsitutions per site.
The mutation-scaled effective sizes ($\epopsize\murate$) of the descendant
populations were gamma-distributed with a shape of 20 and mean of 0.001,
and the size of the ancestral population relative to the mean of its
descendants was gamma distributed with a shape of 50 and mean of 1.
These distributions were also used as priors when the simulated \datasets were
analyzed with \ecoevolity.

When analyzing each simulated \dataset with \ecoevolity,
we ran four MCMC chains for 75,000 generations with a sample taken every 50
generations.
We summarized the last 1000 samples from each chain for a total of 4000 MCMC
samples to approximate the posterior distribution for every simulated \dataset.
From the four chains of each analysis, we calculated the potential
scale reduction factor \citep[PSRF; the square root of Equation 1.1
in][]{Brooks1998} and effective sample size \citep[ESS;][]{Gong2014} for all
continuous parameters and the log likelihood using
\pycoevolity (Version 0.2.6 Commit 27cb15e5).
When plotting results, we highlight any simulation replicates that have a
$\textrm{PSRF} > 1.2$.

\subsubsection{Comparing three models of shared evolutionary events}

We simulated 720 \datasets under five different models of how divergences are
clustered across 10 pairs of populations (3,600 total \datasets).
Each \dataset comprised 500,000 biallelic characters from 2 diploid individuals
per population.
The five models of divergence times were:
\begin{description}
    \item[Simultaneous] All 10 pairs of populations diverged at the same time
        (which was exponentially distributed).
    \item[Independent] All 10 pairs of populations diverged independently.
    \item[DP] Divergence times distributed according to a Dirichlet process
        where the concentration parameter is distributed as
        $\concentration \sim \dgamma{2}{5.42}$.
    \item[PYP] Divergence times distributed according to a Pitman-Yor process
        where the concentration and discount parameters are distributed as
        $\concentration \sim \dgamma{2}{3.58}$
        and
        $\discount \sim \dbeta{1}{4}$.
    \item[\wunif] Divergence times distributed according to a
        weighted-uniform distribution
        where the split-weight parameter is distributed as
        $\splitweight \sim \dgamma{0.55}{4.026}$.
\end{description}
The distributions on the concentration, discount, and split-weight parameters of
the DP, PYP, and \wunif distribution were selected such that the mean number of
divergence events is approximately 5.5
and the probability of each possible number of events
is similar among the three models.

Using \ecoevolity, we analyzed all 3,600 \datasets under the
DP, PYP, and \wunif models both using and excluding invariant characters.
This is a total of
3,600 \datasets $\times$ 3 models $\times$ 2 (with/without invariant characters) $=$ 21,600
analyses, each with four independent MCMC chains as described above.
For prior probability distributions in these analyses,
we used the same distributions described above to generate the data.

\subsubsection{Comparing DP, PYP, and \wunif across \dataset sizes}

To compare the performance of the DP, PYP, and \wunif models as a function of
\dataset size, we simulated 720
\datasets under the ``independent'' model described above, but
with 5,000, 10,000, 50,000, and 100,000 biallelic characters.
We analyzed all 2,880 \datasets under the DP, PYP, and \wunif models
both with and without invariant characters, as
described above.

\subsubsection{An empirical application}

To do \ldots

\section{Results}

\subsection{Analyses of simulated data}

\subsubsection{Comparing three models of shared evolutionary events}

Summary Statistics
Before looking at the results here are some summary statistics that we need to 
understand in order to interpret the results. Coverage or credible sites is the probability
of the number events within the credible sites. The probability of estimated number 
of events equal to the true number of events which basicially tells us how often we 
are right. Median posterior probability is the true number of events given the data 
and this summary statistics tells us how much support we have for the correct answer.
Root mean square error quantifies how much error is there and comparing the true 
value to the estimate value. 
Hyper Parameter Estimation 
We are going to look how well the hyper parameters are estimated. Dirichlet
prior has as a single parameter called concentration parameter that tells how cluster 
the process is. The result of estimated concentration versus true concentration plot
shows that the true value is within 95\% credible sites. Pitman-Yor prior has two 
parameters(concentration parameter and discount parameter) the estimated value of 
concentration versus the true value indicates that the true is also within 95\%
credible sites. The Uniform prior has split weight and the result of estimated value 
versus the true value shows the true value is little less comparing to the other two 
priors but it's still within 94\% credible sites.
In this study, we are interested in divergence time and sharing divergence time and 
everything else is nuisance parameters. For both divergence time and sharing divergence time 
estimation we analyzed data with constant sites and without constant sites. First, we are going 
to look at the results of divegence time estimation with constant sites. The models which generated 
the data in rows and columns represent the models under which the data is analyzed. The true divergene 
time is on x-axis and the estimated divergence time is on y-axis. The results of true divergence 
time versus estimated divengence time show that all the three models (DP, PYP, and SW) performed
equally well with very similiar coverage around 95\%. Except for independent all others have truths 
contianed in within that 95\% credible interval. Independent is little lower because it's evolving 
indepdently and we are not modeling that way. We haven't observed any patterns that differiate
these 3 models. Root mean square errors are very similiar across all the models as well. 
With variable sites only there are more variation in estimates when throwing the invariable 
sites which contain lot of information and when we use them we have much more presicion in estimates
than ingoring them. All 10 pairs diverge spontatnous recently causing some MCMC issues and there 
are very few variable sites all 10 pairs diverged recently. Basicailly there is discrepency bewtween 
gene divergence and population divergence which is the largest at the most recent divergent times.
Comparing the true number of events with estimated number of events among all the sites. The true 
divergence time ranges from 1 to 10 and 1 they all share the divergence time and 10 they all 
diverged independently. The true number of events is the one has the higest posterior probability.
We have 520 replicates and the grid shows how many of them dall in each cell. The result shows 
that the data geenrated under PYP and analyzed under PYP. There are 88 datasets for which the true 
number of divergence is 5 and 76 out of those 88 got the that number correctly. 11 out of 88 
estimated 4 diverngence times and 1 out of 88 estimated 3 divergence time. 
The results for two constraint models all the 3 models under which the data is analyzed show that 
half of the time there are 10 indepedent divergence times for the datasets that is generated under 
indepdent model. The models are doing very well and they got half of time the correct asnwer. The 
ones got wrong are not that far away from the true and they are 8 or 9 event. PYP seems like 
doing little better in terms of how often ge tthe correct answer and also the confident in that 
correct asnwer. The median posterior probability for k=10 getting the correct answer
given the data is 47\% and it's little lower for the other models. The scenario of co-divergence
is an easy scenario and it has the proability of 1 for true number of event versus estimated number of 
event. When the true 1 the models are doing very well estimating the number of divergence time. But 
when the truth is 10 everything is diverging indepdently then it's more difficult scenario for 
modles to handle. Therefore, there is variation in the results. 
The results of true number of events versus estimated number of events among variable sites. The
constant sites are very informative and without invariable sites, the median posterior probability
which is the correct answer is much lower. But the covarage is unaffacted because the 
likelihood for the missing invariable characters is corrected in Ecoevolity. PYP is doing better when 
dealing with the most difficult scenario all the 10 pairs are diverging independetly as well. Both in
terms of covrage and getting the correct answer is much higher than the other two models.

\subsubsection{Comparing DP, PYP, and \wunif across \dataset sizes}

% #### 
% Nuisane Parameters

\subsection{Empirical application?}

\section{Discussion}

\section{Acknowledgments}

We thank \ldots
This work was supported by funding provided to JRO from the National Science
Foundation (NSF grant number DEB 1656004).
The computational work was made possible by the Auburn University (AU) Hopper
Cluster supported by the AU Office of Information Technology
and
a grant of high-performance computing resources and technical support from the
Alabama Supercomputer Authority.
This paper is contribution number \highLight{XXX} of the Auburn University
Museum of Natural History.

%TC:ignore

\bibliographystyle{../bib/evolution}
\bibliography{../bib/references}

\iflinenumbers{
\end{linenumbers}
}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SUPPORTING INFO %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}

\singlespacing

\section*{Supporting Information}
\hangindent=1cm
\noindent Title: \msTitle

\bigskip
{\noindent Authors: \msAuthor}

\newpage
\singlespacing

\input{si-body.tex}
\clearpage

\input{si-tables.tex}
\clearpage

\input{si-figures.tex}

%TC:endignore

\end{document}

### 2021-02-25 manuscript/ms.tex
More work on the model description.

@@
 is the number of ways we can assign \ncomparisons comparisons to
-$1, 2,  \ldots, \ncomparisons$ divergence times
+$\nevents = 1, 2,  \ldots, \ncomparisons$ divergence times
 \citep[the Bell number;][]{Bell1934}.
@@
 divergence events, which we will also refer to as a ``divergence model,'' and
-\etimes to represent the unique divergence times within \etimesets.
+$\etimes = \etime[1], \etime[2], \ldots, \etime[\nevents]$
+to represent the times of the \nevents divergence events.
 
@@
 (i.e., all possible set partitions of \ncomparisons comparisons).
-To get these probabilities, we can assign comparisons to divergence events one
-at a time, following a simple rule.
+To get the probability of any divergence model (\etimesets), we can assign
+comparisons to divergence events one at a time, in any order, following a
+simple rule.
 When assigning the $i^{th}$ comparison, we assign it to its own event
@@
 where $n_x$ is the number of comparisons already assigned to event $x$.
+The overall probability of the divergence model is then the product of each
+comparison's probability of being added to its divergence event.
 \end{linenomath}
@@
 \subsection{Weighted-uniform (\wunif) model}
-We have also implemented a uniform prior over divergence models, where we can
-assume \emph{a priori} that every possible divergence model (\etimesets) is
-equally probable.
-Furthermore, we added a ``split weight'' parameter, which we denote as
-\splitweight, to provide flexibility for the prior probabilities of
-models with different numbers of events.
+We also implemented what we are calling a ``weighted-uniform'' (\wunif) model
+that has a single ``split weight'' parameter that controls the relative
+probability of models with different numbers of events.
 For a given model with \nevents divergence events, the relative probability
@@
 $\frac{1}{\splitweight{}^n}$.
-When $\splitweight = 1$, all divergence models are equally probable.
+Models with the same number of divergence events
+are always equally probable,
+and
+when $\splitweight = 1$, all possible divergence models (\etimesets) across all
+numbers of events are equally probable.
+
+\begin{linenomath}
+To formalize this as a proper probability mass function,
+the probability of any divergence model is
+\begin{equation}
+    p(\etimesets \given \splitweight, \ncomparisons, \nevents) = 
+    \frac{
+        \splitweight^{(\nevents - 1)}
+    }{
+        \sum\limits_{k=1}^{k=\ncomparisons} S_2(\ncomparisons, k) \splitweight^{(k-1)}
+    },
+    \label{eq:uniformdivmodelprob}
+\end{equation}
+where $S_2(\ncomparisons, k)$ is the Stirling number of the second kind which
+is equal to the number of ways of assigning the \ncomparisons comparisons to
+$k$ divergence events.
+\end{linenomath}
 

### 2021-02-26 images/from-project-repo/copy-plots-from-project-repo.sh
Adding plots from project repo.

@@ -1,0 +1,14 @@
+#! /bin/bash
+
+set -e
+
+for plot_file in *.pdf
+do
+    if [[ $plot_file == poster-* ]]
+    then
+        # Skipping images for poster that was already preseented
+        continue
+    fi
+    project_plot_path="../../../ecoevolity-model-prior/results/plots/${plot_file}"
+    cp "$project_plot_path" "$plot_file"
+done

### 2021-02-26 manuscript/ms.tex
Starting to work on results.
Adding a few of the simulation results.

@@
 
+We found that the DP, PYP, and WU models estimated the number of divergence
+events (\nevents) similarly well when applied to \datasets simulated under one
+of the these models (\fig~\ref{fig:neventsgrid}).
+However, when we compare the ability of the models to estimate
+the divergence model (\etimesets), we see that the WU
+model underperforms relative to the DP and PYP models when applied
+to data generated under the DP and PYP models
+(first two rows of \fig~\ref{fig:modeldistancegrid}).
+The DP and PYP models show more robustness when applied to
+data generated under the WU model
+(bottom row of \fig~\ref{fig:modeldistancegrid}).
+
+When applied to \datasets where all 10 pairs of populations diverged
+independently, the PYP model performs slightly better than the other two models
+(top row of \fig~\ref{fig:neventsfixedcomparison}).
+All three models almost always correctly infer a single shared divergence event
+with high posterior probability when it is true
+(bottom row of \fig~\ref{fig:neventsfixedcomparison}).
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-data-rows-nevents-cropped-rasterized.pdf}
+        \captionsetup{listformat=figList}
+        \caption{
+        The models perform similarly in estimating the number of divergence
+        events.
+        Each plot shows the results for 720 \datasets
+        simulated under the
+        DP (top row),
+        PYP (middle row),
+        or
+        WU (bottom row)
+        and analyses using the
+        DP (left column),
+        PYP (middle column),
+        or
+        WU (right column).
+        The number of \datasets that fall within each possible cell of true
+        versus estimated numbers of events is shown, and cells with more
+        \datasets are shaded darker.
+        % The estimates are based on the number of events with the maximum
+        % \textit{a posteriori} (MAP) probability.
+        Above each plot is
+        the proportion of \datasets for which the number of events with the largest
+        posterior probability matched the true number of events---$p(\hat{\nevents}
+        = \nevents)$,
+        the median posterior probability of the correct number of events across all
+        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
+        the proportion of \datasets for which the true number of events was
+        included in the 95\% credible set---$p(\nevents \in
+        \textrm{CS})$.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:neventsgrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-data-rows-model-distance-box-cropped.pdf}
+        \captionsetup{listformat=figList}
+        \caption{
+        Comparing the models' ability to estimate the divergence model.
+        Each plot shows posterior mean distances from the true model
+        for 720 \datasets
+        simulated under the
+        DP (top row),
+        PYP (middle row),
+        or
+        WU (bottom row)
+        and analyses using the
+        DP (left column),
+        PYP (middle column),
+        or
+        WU (right column).
+        % The estimates are based on the number of events with the maximum
+        % \textit{a posteriori} (MAP) probability.
+        The mean model distance across all 720 analyses is shown at the top of
+        each plot.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:modeldistancegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-fixed-rows-nevents-cropped.pdf}
+        \captionsetup{listformat=figList}
+        \caption{
+        The PYP (middle column) model performs better than the DP (left column)
+        and WU (right column) models when analyzing simulated \datasets for
+        which all 10 population pairs diverged independently (top row).
+        All three models almost always correctly infer a single shared
+        divergence event with high confidence when analyzing simulated
+        \datasets for which that is true (bottom row).
+        Each plot shows the results for 720 \datasets.
+        Above each plot is
+        the proportion of \datasets for which the number of events with the largest
+        posterior probability matched the true number of events---$p(\hat{\nevents}
+        = \nevents)$,
+        the median posterior probability of the correct number of events across all
+        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
+        the proportion of \datasets for which the true number of events was
+        included in the 95\% credible set---$p(\nevents \in
+        \textrm{CS})$.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:neventsfixedcomparison}
+    \end{center}
+\end{figure}
+
 Summary Statistics

### 2021-03-02 manuscript/ms.tex
Adding bib files in ms directory.
Overleaf cannot seem to handle the bib/bst files being in a different
directory from the main tex file, so adding copies to the manuscript
directory. Not cool at all.
Working on incorporating new plots into ms.
Also, adding references.

--- 2021-02-25 manuscript/ms.tex
@@
 
+We found that the DP, PYP, and WU models estimated the number of divergence
+events (\nevents) similarly well when applied to \datasets simulated under one
+of the these models (\fig~\ref{fig:neventsgrid}).
+However, when we compare the ability of the models to estimate
+the divergence model (\etimesets), we see that the WU
+model underperforms relative to the DP and PYP models when applied
+to data generated under the DP and PYP models
+(first two rows of \fig~\ref{fig:modeldistancegrid}).
+The DP and PYP models show more robustness when applied to
+data generated under the WU model
+(bottom row of \fig~\ref{fig:modeldistancegrid}).
+
+When applied to \datasets where all 10 pairs of populations diverged
+independently, the PYP model performs slightly better than the other two models
+(top row of \fig~\ref{fig:neventsfixedcomparison}).
+All three models almost always correctly infer a single shared divergence event
+with high posterior probability when it is true
+(bottom row of \fig~\ref{fig:neventsfixedcomparison}).
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/model-performance-violin-cropped.pdf}
+        \captionsetup{listformat=figList}
+        \caption{
+        Comparing the models' ability to estimate the divergence model.
+        Each column of plots compares the performance of the Dirichlet process
+        (DP), Pitman-Yor process (PYP) and weighted-uniform (WU) models when
+        analyzing 720 \datasets simulated under the (from left-to-right)
+        simultaneous-divergence, DP, PYP, WU, and independent-divergences
+        model. 
+        The first row shows the mean distance from the true
+        divergence model (\etimesets) of the posterior samples
+        \citep{Kuhn1955,Munkres1957,Gusfield2002} calculated
+        using Version 1.1.4 of the munkres Python package
+        \citep{Clapper2020}.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:modeldistancegrid}
+    \end{center}
+\end{figure}
+
 Summary Statistics
@@
 
-\bibliographystyle{../bib/evolution}
-\bibliography{../bib/references}
+\bibliographystyle{evolution}
+\bibliography{references}
 

### 2021-03-02 manuscript/si-figures.tex
Working on incorporating new plots into ms.
Also, adding references.

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-data-rows-nevents-cropped-rasterized.pdf}
        \captionsetup{listformat=sFigList}
        \caption{
        The models perform similarly in estimating the number of divergence
        events.
        Each plot shows the results for 720 \datasets
        simulated under the
        DP (top row),
        PYP (middle row),
        or
        WU (bottom row)
        and analyses using the
        DP (left column),
        PYP (middle column),
        or
        WU (right column).
        The number of \datasets that fall within each possible cell of true
        versus estimated numbers of events is shown, and cells with more
        \datasets are shaded darker.
        % The estimates are based on the number of events with the maximum
        % \textit{a posteriori} (MAP) probability.
        Above each plot is
        the proportion of \datasets for which the number of events with the largest
        posterior probability matched the true number of events---$p(\hat{\nevents}
        = \nevents)$,
        the median posterior probability of the correct number of events across all
        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
        the proportion of \datasets for which the true number of events was
        included in the 95\% credible set---$p(\nevents \in
        \textrm{CS})$.
        We generated the plot using matplotlib Version 3.1.3
        \citep{matplotlib}.
        }
        \label{fig:neventsgrid}
    \end{center}
\end{figure}

\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-fixed-rows-nevents-cropped.pdf}
        \captionsetup{listformat=sFigList}
        \caption{
        The PYP (middle column) model performs better than the DP (left column)
        and WU (right column) models when analyzing simulated \datasets for
        which all 10 population pairs diverged independently (top row).
        All three models almost always correctly infer a single shared
        divergence event with high confidence when analyzing simulated
        \datasets for which that is true (bottom row).
        Each plot shows the results for 720 \datasets.
        Above each plot is
        the proportion of \datasets for which the number of events with the largest
        posterior probability matched the true number of events---$p(\hat{\nevents}
        = \nevents)$,
        the median posterior probability of the correct number of events across all
        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
        the proportion of \datasets for which the true number of events was
        included in the 95\% credible set---$p(\nevents \in
        \textrm{CS})$.
        We generated the plot using matplotlib Version 3.1.3
        \citep{matplotlib}.
        }
        \label{fig:neventsfixedcomparison}
    \end{center}
\end{figure}

### 2021-03-03 manuscript/ms.tex
Working on manuscript.
Adding methods subsection about how we quantify model performance.
Incorporating better plots from main project repo and relegating
other plots to the supporting info.

--- 2021-02-25 manuscript/ms.tex
@@
 \author[1]{Tashitso Anamza}
+\author[1]{Tanner Myers}
+\author[1]{Randy Klabacka}
+\author[1]{Perry L.\ Wood, Jr.}
+\author[1]{Claire Tracy}
+\author[1]{Kerry Cobb}
+\author[1]{Matthew Buehler}
 \author[1]{Jamie R.\ Oaks \thanks{Corresponding author: \href{mailto:joaks@auburn.edu}{\tt joaks@auburn.edu}}}
@@
 
-\subsubsection{An empirical application}
+\subsubsection{Quantifying the performance on simulated data}
+
+The primary goal of methods like \ecoevolity is to infer the number of
+divergence events and the assignment of the comparisons to those events
+(\etimesets).
+To quantify the error in estimating \etimesets from each simulated \dataset, we
+used the partition distance between the true \etimesets and those sampled from
+the posterior distribution of the DP, PYP, and \wunif models
+\citep{Regnier1983,Gusfield2002}.
+In our context, the partition distance between the true and sampled \etimesets
+is the minimum number of divergence comparisons that need to be removed for the
+assignment of the remaining comparisons to divergence events to match between
+the two \etimesets.
+% Below we will refer to this distance as \etimesets error.
+To calculate this distance we used the Hungarian (or Kuhn-Munkres) algorithm
+\citep{Kuhn1955,Munkres1957}
+as implemented in Version 1.1.4 of the Munkres Python package
+\citep{Clapper2020}.
+
+In addition to partition distances as metric for \etimesets error, we used
+three additional statistics to quantify performance in estimating \etimesets:
+$p(\hat{\etimesets} =\etimesets)$---
+    the proportion of simulation replicates in which the true \etimesets had
+    the maximum posterior probability,
+% However, this metric can be misleading.
+% For example, in our simultaneous-divergence and independent-divergence simulations,
+% the true divergence model has the maximum prior probability simply because there
+% is only a single model with one and 10 divergences.
+% Thus, if the data provide no information, there is a 50\% chance of the true
+% model having the maximum posterior probability.
+$p(\etimesets \given \alldata)$---
+    the posterior probability of the true divergence model,
+and
+$p(\etimesets \in \textrm{95\% CS})$---
+    the proportion of simulation replicates for which he true \etimesets is
+    included in the 95\% posterior credibility set of divergence models (i.e.,
+    coverage).
+
+\subsection{An empirical application}
 
@@
 \subsubsection{Comparing three models of shared evolutionary events}
+
+When we compare the error in estimating the divergence model (\etimesets) and
+the posterior support for the true \etimesets, we see that the WU model
+underperforms relative to the DP and PYP models when applied to data generated
+under the simultaneous, DP, and PYP models
+(first two rows of \fig~\ref{fig:modelperformancegrid}).
+The DP and PYP models show more robustness when applied to
+data generated under the WU model.
+As expected, we find the simulations where all 10 pairs diverged independently
+to be the most challenging scenario for all three models.
+The PYP model performs better than the DP and \wunif model
+when analyzing these most challenging \datasets
+(right-most column of \fig~\ref{fig:modelperformancegrid}).
+This is true across all of the \dataset sizes we simulated
+under the independent-divergences model
+(\fig~\ref{fig:modelperformancebysize})
+However, the differences in performance are small and the order of the three
+models mirror the prior probability they place on the independent-divergences
+model.
+
+We see similar, albeit more subtle, patterns when we look at the estimated
+number of divergence events
+(\figs S\ref{fig:neventsgrid} and S\ref{fig:neventsfixedcomparison}).
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/model-performance-violin-cropped.pdf}
+        \captionsetup{listformat=figList}
+        \caption{
+        Comparing the models' ability to estimate the divergence model.
+        Each column of plots compares the performance of the Dirichlet process
+        (DP), Pitman-Yor process (PYP) and weighted-uniform (WU) models when
+        analyzing 720 \datasets simulated under the (from left-to-right)
+        simultaneous-divergence, DP, PYP, WU, and independent-divergences
+        model. 
+        Mean \etimesets error is the mean partition distance
+        of the posterior samples from the true
+        divergence model (\etimesets),
+        $p(\etimesets \given \alldata)$ is the posterior probability
+        of the true divergence model,
+        $p(\etimesets \given \alldata)$ is the posterior probability of the
+        true divergence model,
+        and
+        $p(\etimesets \in \textrm{95\% CS})$ is the proportion of simulation
+        replicates for which he true \etimesets is included in the 95\%
+        posterior credibility set of divergence models.
+        The bars overlaying the violin plots show the interval between the
+        2.5\% and 97.5\% percentiles, and the white dot is the median.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:modelperformancegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/nchars-model-performance-violin-cropped.pdf}
+        \captionsetup{listformat=figList}
+        \caption{
+        Comparing the models' ability to estimate the independent-divergence
+        model as the \dataset size increases.
+        Each column of plots compares the performance of the Dirichlet process
+        (DP), Pitman-Yor process (PYP) and weighted-uniform (WU) models when
+        analyzing 720 \datasets with 5,000 to 500,000 characters simulated
+        under the independent-divergences model
+        Mean \etimesets error is the mean partition distance
+        of the posterior samples from the true
+        divergence model (\etimesets),
+        $p(\etimesets \given \alldata)$ is the posterior probability
+        of the true divergence model,
+        $p(\etimesets \given \alldata)$ is the posterior probability of the
+        true divergence model,
+        and
+        $p(\etimesets \in \textrm{95\% CS})$ is the proportion of simulation
+        replicates for which he true \etimesets is included in the 95\%
+        posterior credibility set of divergence models.
+        The bars overlaying the violin plots show the interval between the
+        2.5\% and 97.5\% percentiles, and the white dot is the median.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:modelperformancebysize}
+    \end{center}
+\end{figure}
 

### 2021-03-04 manuscript/ms.tex
Working on results of manuscript.
Adding plots of div time and pop size parameters.

@@
 under the independent-divergences model
-(\fig~\ref{fig:modelperformancebysize})
+(\fig~\ref{fig:modelperformancebysize}).
 However, the differences in performance are small and the order of the three
@@
 
-We see similar, albeit more subtle, patterns when we look at the estimated
+We see similar patterns in the relative performance of the DP, PYP, and
+\wunif models when only the variable characters from the simulated
+\datasets are analyzed
+(\figs S\ref{fig:varonlymodelperformancegrid}
+and S\ref{fig:varonlymodelperformancebysize}).
+However, the performance of all three models is greatly reduced when
+only variable characters are used,
+which is consistent with the findings of
+\citet{Oaks2018ecoevolity,Oaks2018paic,Oaks2019codemog}.
+We also see similar patterns when we look at the estimated
 number of divergence events
-(\figs S\ref{fig:neventsgrid} and S\ref{fig:neventsfixedcomparison}).
+(\figs S\labelcref{fig:neventsgrid,fig:varonlyneventsgrid,fig:neventsfixedcomparison,fig:varonlyneventsfixedcomparison,fig:neventsgridbysize,fig:varonlyneventsgridbysize}), however, many of the patterns are more
+suitable when compared to the
+
+All three models performed similarly in estimating the divergence times and
+effective sizes of the ancestral and descendant populations
+across all of our simulations
+(\figs S\labelcref{fig:divtimegrid,fig:varonlydivtimegrid,fig:divtimegridbysize,fig:varonlydivtimegridbysize,fig:ancpopsizegrid,fig:varonlyancpopsizegrid,fig:ancpopsizegridbysize,fig:varonlyancpopsizegridbysize,fig:descpopsizegrid,fig:varonlydescpopsizegrid,fig:descpopsizegridbysize,fig:varonlydescpopsizegridbysize}).
+As found previously \citep{Oaks2018ecoevolity,Oaks2018paic,Oaks2019codemog}, using invariant characters results in much greater precision
+in these estimates
+(\figs S\labelcref{fig:divtimegrid,fig:varonlydivtimegrid,fig:divtimegridbysize,fig:varonlydivtimegridbysize,fig:ancpopsizegrid,fig:varonlyancpopsizegrid,fig:ancpopsizegridbysize,fig:varonlyancpopsizegridbysize,fig:descpopsizegrid,fig:varonlydescpopsizegrid,fig:descpopsizegridbysize,fig:varonlydescpopsizegridbysize}).
 
@@
         analyzing 720 \datasets with 5,000 to 500,000 characters simulated
-        under the independent-divergences model
+        under the independent-divergences model.
         Mean \etimesets error is the mean partition distance

### 2021-03-04 manuscript/si-figures.tex
Working on manuscript.
Adding methods subsection about how we quantify model performance.
Incorporating better plots from main project repo and relegating
other plots to the supporting info.
Working on results of manuscript.
Adding plots of div time and pop size parameters.

@@
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/var-only-model-performance-violin-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{
+        Comparing the models' ability to estimate the divergence model
+        when using only variable characters from simulated \datasets.
+        Each column of plots compares the performance of the Dirichlet process
+        (DP), Pitman-Yor process (PYP) and weighted-uniform (\wunif) models when
+        analyzing only variable characters from 720 \datasets simulated under
+        the (from left-to-right) simultaneous-divergence, DP, PYP, \wunif, and
+        independent-divergences model. 
+        Mean \etimesets error is the mean partition distance
+        of the posterior samples from the true
+        divergence model (\etimesets),
+        $p(\etimesets \given \alldata)$ is the posterior probability
+        of the true divergence model,
+        $p(\etimesets \given \alldata)$ is the posterior probability of the
+        true divergence model,
+        and
+        $p(\etimesets \in \textrm{95\% CS})$ is the proportion of simulation
+        replicates for which he true \etimesets is included in the 95\%
+        posterior credibility set of divergence models.
+        The bars overlaying the violin plots show the interval between the
+        2.5\% and 97.5\% percentiles, and the white dot is the median.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlymodelperformancegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/var-only-nchars-model-performance-violin-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{
+        Comparing the models' ability to estimate the independent-divergence
+        model when using only variable characters from \datasets of different
+        sizes.
+        Each column of plots compares the performance of the Dirichlet process
+        (DP), Pitman-Yor process (PYP) and weighted-uniform (\wunif) models when
+        analyzing only variable characters from 720 \datasets with 5,000 to
+        500,000 characters simulated under the independent-divergences model.
+        Mean \etimesets error is the mean partition distance
+        of the posterior samples from the true
+        divergence model (\etimesets),
+        $p(\etimesets \given \alldata)$ is the posterior probability
+        of the true divergence model,
+        $p(\etimesets \given \alldata)$ is the posterior probability of the
+        true divergence model,
+        and
+        $p(\etimesets \in \textrm{95\% CS})$ is the proportion of simulation
+        replicates for which he true \etimesets is included in the 95\%
+        posterior credibility set of divergence models.
+        The bars overlaying the violin plots show the interval between the
+        2.5\% and 97.5\% percentiles, and the white dot is the median.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlymodelperformancebysize}
+    \end{center}
+\end{figure}
+
 \begin{figure}[htbp]
@@
         \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-data-rows-nevents-cropped-rasterized.pdf}
-        \captionsetup{listformat=sFigList}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
         \caption{
@@
         or
-        WU (bottom row)
+        \wunif (bottom row)
         and analyses using the
@@
         or
-        WU (right column).
+        \wunif (right column).
         The number of \datasets that fall within each possible cell of true
@@
     \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/var-only-infer-columns-by-data-rows-nevents-cropped-rasterized.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{
+        The models perform similarly in estimating the number of divergence
+        events when using only variable characters from the simulated
+        \datasets.
+        Each plot shows the results from using only variable characters from
+        720 \datasets simulated under the
+        DP (top row),
+        PYP (middle row),
+        or
+        \wunif (bottom row)
+        and analyses using the
+        DP (left column),
+        PYP (middle column),
+        or
+        \wunif (right column).
+        The number of \datasets that fall within each possible cell of true
+        versus estimated numbers of events is shown, and cells with more
+        \datasets are shaded darker.
+        % The estimates are based on the number of events with the maximum
+        % \textit{a posteriori} (MAP) probability.
+        Above each plot is
+        the proportion of \datasets for which the number of events with the largest
+        posterior probability matched the true number of events---$p(\hat{\nevents}
+        = \nevents)$,
+        the median posterior probability of the correct number of events across all
+        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
+        the proportion of \datasets for which the true number of events was
+        included in the 95\% credible set---$p(\nevents \in
+        \textrm{CS})$.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlyneventsgrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
         \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-fixed-rows-nevents-cropped.pdf}
-        \captionsetup{listformat=sFigList}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
         \caption{
         The PYP (middle column) model performs better than the DP (left column)
-        and WU (right column) models when analyzing simulated \datasets for
+        and \wunif (right column) models when analyzing simulated \datasets for
         which all 10 population pairs diverged independently (top row).
@@
 \end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/var-only-infer-columns-by-fixed-rows-nevents-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{
+        The PYP (middle column) model performs better than the DP (left column)
+        and \wunif (right column) models when analyzing only variable characters
+        from simulated \datasets for which all 10 population pairs diverged
+        independently (top row).
+        All three models perform well at correctly infer a single shared
+        divergence event when analyzing simulated \datasets for which that is
+        true (bottom row), although the \wunif model does not perform quite as
+        well as the DP and PYP models.
+        Each plot shows the results from using only variable characters from
+        720 \datasets.
+        Above each plot is
+        the proportion of \datasets for which the number of events with the largest
+        posterior probability matched the true number of events---$p(\hat{\nevents}
+        = \nevents)$,
+        the median posterior probability of the correct number of events across all
+        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
+        the proportion of \datasets for which the true number of events was
+        included in the 95\% credible set---$p(\nevents \in
+        \textrm{CS})$.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlyneventsfixedcomparison}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/nchars-nevents-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\scriptsize
+        The PYP (middle column) model performs better than the DP (left column)
+        and \wunif (right column) models when analyzing \datasets of different
+        sizes simulated under the independent-divergences model.
+        Each plot shows the results for 720 \datasets with 5,000 to
+        500,000 characters simulated under the independent-divergences model.
+        Above each plot is
+        the proportion of \datasets for which the number of events with the largest
+        posterior probability matched the true number of events---$p(\hat{\nevents}
+        = \nevents)$,
+        the median posterior probability of the correct number of events across all
+        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
+        the proportion of \datasets for which the true number of events was
+        included in the 95\% credible set---$p(\nevents \in
+        \textrm{CS})$.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:neventsgridbysize}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/var-only-nchars-nevents-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\scriptsize
+        The PYP (middle column) model performs better than the DP (left column)
+        and \wunif (right column) models when analyzing only variable characters
+        from \datasets of different sizes simulated under the
+        independent-divergences model.
+        Each plot shows the results from 720 \datasets when analyzing only the
+        variable characters out of 5,000 to 500,000 characters simulated under
+        the independent-divergences model.
+        Above each plot is
+        the proportion of \datasets for which the number of events with the largest
+        posterior probability matched the true number of events---$p(\hat{\nevents}
+        = \nevents)$,
+        the median posterior probability of the correct number of events across all
+        \datasets---$\widetilde{p(\nevents|\alldata)}$, and
+        the proportion of \datasets for which the true number of events was
+        included in the 95\% credible set---$p(\nevents \in
+        \textrm{CS})$.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlyneventsgridbysize}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-data-rows-div-time-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly well at estimating the divergence times from
+        \datasets simulated under five different models (see row labels) with
+        500,000 characters from 10 pairs of populations.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true divergence time was
+        included in the 95\% credible interval---$p(\comparisonetime \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:divtimegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/var-only-infer-columns-by-data-rows-div-time-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the divergence times from only the
+        variable characters from \datasets simulated under five different
+        models (see row labels) with 10 pairs of populations.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true divergence time was
+        included in the 95\% credible interval---$p(\comparisonetime \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlydivtimegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/nchars-div-time-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly well at estimating the divergence times from
+        \datasets of varying size (see row labels) simulated with
+        10 pairs of populations diverging independently.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true divergence time was
+        included in the 95\% credible interval---$p(\comparisonetime \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:divtimegridbysize}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/var-only-nchars-div-time-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the divergence times from only the
+        variable characters from \datasets of varying size (see row labels)
+        simulated with 10 pairs of populations diverging independently.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true divergence time was
+        included in the 95\% credible interval---$p(\comparisonetime \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlydivtimegridbysize}
+    \end{center}
+\end{figure}
+
+% Ancestral population size
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-data-rows-ancestor-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the effective size of the
+        ancestral populations from \datasets simulated under five different
+        models (see row labels) with 500,000 characters from 10 pairs of
+        populations.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:ancpopsizegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/var-only-infer-columns-by-data-rows-ancestor-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the effective size of the ancestral
+        populations from only the variable characters from \datasets simulated
+        under five different models (see row labels) with 10 pairs of
+        populations.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlyancpopsizegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/nchars-ancestor-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly well at estimating the effective size of the
+        ancestral populations from \datasets of varying size (see row labels)
+        simulated with 10 pairs of populations diverging independently.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:ancpopsizegridbysize}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/var-only-nchars-ancestor-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the effective size of the ancestral
+        populations from only the variable characters from \datasets of varying
+        size (see row labels) simulated with 10 pairs of populations diverging
+        independently.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlyancpopsizegridbysize}
+    \end{center}
+\end{figure}
+
+% Descendant population size
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/infer-columns-by-data-rows-descendant-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the effective size of the
+        descendant populations from \datasets simulated under five different
+        models (see row labels) with 500,000 characters from 10 pairs of
+        populations.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:descpopsizegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/var-only-infer-columns-by-data-rows-descendant-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the effective size of the descendant
+        populations from only the variable characters from \datasets simulated
+        under five different models (see row labels) with 10 pairs of
+        populations.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlydescpopsizegrid}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/nchars-descendant-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly well at estimating the effective size of the
+        descendant populations from \datasets of varying size (see row labels)
+        simulated with 10 pairs of populations diverging independently.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:descpopsizegridbysize}
+    \end{center}
+\end{figure}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=0.9\textheight,keepaspectratio]{../images/from-project-repo/var-only-nchars-descendant-size-scatter-cropped.pdf}
+        \captionsetup{name=Figure S, labelformat=noSpace, listformat=sFigList}
+        \caption{\footnotesize
+        The DP (left column),
+        PYP (middle column),
+        and
+        \wunif
+        perform similarly at estimating the effective size of the descendant
+        populations from only the variable characters from \datasets of varying
+        size (see row labels) simulated with 10 pairs of populations diverging
+        independently.
+        At the top of each plot is the root-mean-square error (RMSE)
+        and
+        the proportion of \datasets for which the true population size was
+        included in the 95\% credible interval---$p(\epopsize\murate \in
+        \textrm{CS})$.
+        Estimates for which the potential-scale reduction factor was greater
+        than 1.2 \citep{Brooks1998} are highlighted in orange.
+        We generated the plot using matplotlib Version 3.1.3
+        \citep{matplotlib}.
+        }
+        \label{fig:varonlydescpopsizegridbysize}
+    \end{center}
+\end{figure}

### 2021-09-21 manuscript/ms.tex
Update on Overleaf.

@@
 \begin{abstract}
-    Abstract here \ldots
+Evolutionary biologists are interested in investigating the evolutionary history of the species.
+Models are one of the means that allow them to model the world or the evolutionary processes.
+Therefore, knowing the behavior of the models is important.
+This study compares the performance of three models Dirichlet process, Pitman-Yor process, and weighted-uniform(DP, PYP, and WU) that are implemented in \ecoevolity software to estimate the number of shared divergence time among 10 pairs of population in the past.
+Our results show that Pitman-Yor process which is the more flexible model, consistently outperforms the other two models in both simulations (with reduced data sets).
+The flexibility of Pitman-Yor process has some advantages, especially when it is wrong.
 
     \vspace{6pt}
-    \noindent\textbf{KEY WORDS:}
+    \noindent\textbf{KEY WORDS:Phylogeography, divergence time, evolutionary events, Dirichlet process, Pitman-Yor process, weighted-uniform process, the behavior of models.}
+
 \end{abstract}
@@
 \section{Introduction}
+Rewrite Intro because it's kind of overlapping with the result section.
 
-In this study, we compared the performance of 3 models (Dirichlet prior, Pitman-Yor prior and Uniform prior) 
+Phylogeographic Study \\
+Sharing divergence time across taxa \\
+Shared divergence across taxa happened via geological events. \\
+Temporal clustering reveals evolutionary history of the taxa. \\
+Temporal pattern- \\
+Model the evolutionary process \\
+Important to know the behavior of the models \\
+Evolutionary events
+
+We compared the performance of 3 models (Dirichlet prior, Pitman-Yor prior and Uniform prior) 
 that are implemented in Ecoevolity software which is the primary software we used to estimate the number of shared divergence time 
@@
 and have some sense of comparison. We are interested in how well the models have estimated the divergence time and how well 
-the models have estimated what population pairs belong to which divergence time.
-
-Before going further we needed to assign prior probabilities to 3 models; how probable each model is. Dirichlet-process prior 
-assigns prior to a new category with probability of \[\frac{1}{a+1}\] and an exsiting category with probability of \[\frac{a}{a+1}\]. The concentration parameter(a) 
+the models have estimated what population pairs belong to which divergence time. We assigned prior probabilities to 3 models; how probable each model is. Dirichlet-process prior 
+assigns prior to a new category with probability of \(\dfrac{1}{\concentration +1}\) and an existing category with probability of \(\dfrac{\concentration}{\concentration+1}\).
+The concentration parameter(\concentration)
 makes the DP flexible because we can adjust the concentration parameter to fit our prior expectation. We can put a distribution on the 
-concetration parameter and integrate over uncertainty about the prior probabilities of the divergence models. Pitman-Yor process prior is 
-generalization of Dirichlet process. There is a discount parameter(d) added in PYP and when d=0 PYP converges to DP. Dirichlet has an exponential tail 
-and the discount parameter gives the PYP flexibity over the tail behavior. Uniform prior is every possible divergence model is equally probable. 
+concentration parameter and integrate over uncertainty about the prior probabilities of the divergence models. Pitman-Yor process prior is 
+generalization of Dirichlet process. There is a discount parameter($\discount$) added in PYP and when $\discount= 0$ PYP converges to DP. Dirichlet has an exponential tail 
+and the discount parameter gives the PYP flexibility over the tail behavior. Uniform prior is every possible divergence model is equally probable. 
 Then we have specified the priors in the config files for each of these 3 models that they are comparable to each other to assess the behavior of the models.
 
-We used these 3 config files and then added 2 more configs (independent and simutanous configs ) to simulate datasets. Independent config 
-basically spefifies there are 10 divergence times and each population diverged independently. Simutanous config specifies that the populations 
-diverged simutanously and there is 1 shared event. And there is another config file which ignores the constant sites(characters). A total of 6 config 
-files are specified to simulate the datasets. We used these 6 config files 4 times to generate scripts and then simulated 10 datasets under each of 
+We used these 3 config files and then added 2 more configs (independent and simutanous configs) to simulate data sets. Independent config 
+basically specifies 10 divergence times and each population diverged independently. Simutanous config specifies that the populations 
+diverged simutanously and there is 1 shared event. And there is another config file which ignores the constant sites (characters). A total of 6 config 
+files are specified to simulate the data sets. We used these 6 config files 4 times to generate scripts and then simulated 10 data sets under each of 
 these 5 models with 5000,000 characters. Then we analyzed the data under 3 models and the results show that Pitman-Yor process is doing better job handling 
-most difficult scenario all 10 pairs diverging independetly because PYP is more flexible model. The coverage is more robust for Pitman-Yor process twice likely.
-So we are interested to see whether this pattern holds with less data. We decided to do another simulation with 4 varying datasets 5,000, 10,000, 50,000, and 100,000. 
-All the datasets simulated under 5 models and then analyzed these datasets under 3 models (DP, PYP, and SW). There are equal number of replicates for both simulations 
-a total of 720 replicates for each simulation. We found that with varying datasets suggest the same Pitman-Yor process has 2 parameters and more flexible might 
+most difficult scenario all 10 pairs diverged independently because PYP is more flexible model. The coverage is more robust for Pitman-Yor process twice likely.
+So we are interested to see whether this pattern holds with less data. We decided to do another simulation with 4 varying data sets 5,000, 10,000, 50,000, and 100,000. 
+All the data sets simulated under 5 models and then analyzed these data sets under 3 models (DP, PYP, and SW). There are equal number of replicates for both simulations 
+a total of 720 replicates for each simulation. We found that with varying data sets suggest the same Pitman-Yor process has 2 parameters and more flexible might 
 have some advantages especially when it is wrong.
@@
 \end{enumerate}
-For simplicity, we will use terminology related to divergence comparions, but
+For simplicity, we will use terminology related to divergence comparisons, but
 all of the theory discussed below also applies to demographic comparisons.
@@
 $p(\etimesets \in \textrm{95\% CS})$---
-    the proportion of simulation replicates for which he true \etimesets is
+    the proportion of simulation replicates for which the true \etimesets is
     included in the 95\% posterior credibility set of divergence models (i.e.,
@@
         $p(\etimesets \in \textrm{95\% CS})$ is the proportion of simulation
-        replicates for which he true \etimesets is included in the 95\%
+        replicates for which the true \etimesets is included in the 95\%
         posterior credibility set of divergence models.
@@
 
-Summary Statistics
-Before looking at the results here are some summary statistics that we need to 
-understand in order to interpret the results. Coverage or credible sites is the probability
-of the number events within the credible sites. The probability of estimated number 
-of events equal to the true number of events which basicially tells us how often we 
+A description of some summary statistics that will help us to interpret the results. Coverage or credible sites is the probability
+of the number of events within the credible sites. The probability of estimated number 
+of events equal to the true number of events which basically tells us how often we 
 are right. Median posterior probability is the true number of events given the data 
@@
 Comparing the true number of events with estimated number of events among all the sites. The true 
-divergence time ranges from 1 to 10 and 1 they all share the divergence time and 10 they all 
-diverged independently. The true number of events is the one has the higest posterior probability.
-We have 520 replicates and the grid shows how many of them dall in each cell. The result shows 
-that the data geenrated under PYP and analyzed under PYP. There are 88 datasets for which the true 
+divergence time ranges from 1 to 10.  1 refers they all share the divergence time and 10 means they all 
+diverged independently. The true number of events is the one has the highest posterior probability.
+We have 520 replicates and the grid shows how many of them are in each cell. The result shows 
+that the data generated under PYP and analyzed under PYP. There are 88 data sets for which the true 
 number of divergence is 5 and 76 out of those 88 got the that number correctly. 11 out of 88 
-estimated 4 diverngence times and 1 out of 88 estimated 3 divergence time. 
+estimated 4 divergence times and 1 out of 88 estimated 3 divergence time. 
 The results for two constraint models all the 3 models under which the data is analyzed show that 
-half of the time there are 10 indepedent divergence times for the datasets that is generated under 
-indepdent model. The models are doing very well and they got half of time the correct asnwer. The 
+half of the time there are 10 independent divergence times for the data sets that is generated under 
+independent model. The models are doing very well and they got half of time the correct answer. The 
 ones got wrong are not that far away from the true and they are 8 or 9 event. PYP seems like 
-doing little better in terms of how often ge tthe correct answer and also the confident in that 
-correct asnwer. The median posterior probability for k=10 getting the correct answer
+doing little better in terms of how often get the correct answer and also the confident in that 
+correct answer. The median posterior probability for k=10 getting the correct answer
 given the data is 47\% and it's little lower for the other models. The scenario of co-divergence
-is an easy scenario and it has the proability of 1 for true number of event versus estimated number of 
-event. When the true 1 the models are doing very well estimating the number of divergence time. But 
-when the truth is 10 everything is diverging indepdently then it's more difficult scenario for 
-modles to handle. Therefore, there is variation in the results. 
+is an easy scenario and it has the probability of 1 for true number of event versus estimated number of 
+event. When the truth is 1 the models are doing very well estimating the number of divergence time. But 
+when the truth is 10 everything is diverging independently then it's more difficult scenario for 
+models to handle. Therefore, there is variation in the results. 
 The results of true number of events versus estimated number of events among variable sites. The
 constant sites are very informative and without invariable sites, the median posterior probability
-which is the correct answer is much lower. But the covarage is unaffacted because the 
-likelihood for the missing invariable characters is corrected in Ecoevolity. PYP is doing better when 
-dealing with the most difficult scenario all the 10 pairs are diverging independetly as well. Both in
-terms of covrage and getting the correct answer is much higher than the other two models.
+which is the correct answer is much lower. But the coverage is unaffected because the 
+likelihood for the missing invariable characters is corrected in \Ecoevolity. PYP is doing better when 
+dealing with the most difficult scenario all the 10 pairs are diverging independently as well. Both in
+terms of coverage and getting the correct answer is much higher than the other two models.
 

### 2022-06-06 manuscript/ms.tex
Update on Overleaf.

@@
 Evolutionary biologists are interested in investigating the evolutionary history of the species.
-Models are one of the means that allow them to model the world or the evolutionary processes.
+phylogenetic models are one of the means that allow them to model the world or the evolutionary processes that are responsible for generating biodiversity patterns across the tree of life.
+These models also be able to predict or test the primary mechanism for population divergence.
 Therefore, knowing the behavior of the models is important.
-This study compares the performance of three models Dirichlet process, Pitman-Yor process, and weighted-uniform(DP, PYP, and WU) that are implemented in \ecoevolity software to estimate the number of shared divergence time among 10 pairs of population in the past.
-Our results show that Pitman-Yor process which is the more flexible model, consistently outperforms the other two models in both simulations (with reduced data sets).
+This study compares the performance of three models Dirichlet process, Pitman-Yor process, and weighted-uniform(DP, PYP, and WU) that are implemented in \ecoevolity software to estimate the number of shared divergence time among 10 pairs of population in the past.Our results show that Pitman-Yor process which is the more flexible model, consistently outperforms the other two models in both simulations (with reduced data sets).
 The flexibility of Pitman-Yor process has some advantages, especially when it is wrong.
@@
 \section{Introduction}
-Rewrite Intro because it's kind of overlapping with the result section.
+The primary goal of biogeography is to understand how the large-scale evolutionary processes like climate change affect the diversification.
+Evolutionary processes have a large effect on the diversity and diversification of the species.
+Biogeographers are interested in knowing the biogeographic patterns among the co-distributed species.
+How these large-scale evolutionary processes affect the species' evolutionary history and what kind of roles these evolutionary processes play in creating the biodiversity patterns across the taxa.
+Climate change is one of processes that shapes the evolutionary history of the species.
+Climate fluctuated through the earth's history from warming to cold, glaciation to deglaciation, and arise in sea level vice verse.
+For some species, climate-driven mechanism is the primary mode of population divergence \citep{Oaks2019codemogpreprint}.\\ Phylogenetic models allow to capture micro and macroevolutionary processes that have generated biodiversity patterns across the tree of life \citep{Oaks2022}.
+Various phylogenetic models from generalized tree model to process-based models can be utilized to predict or test for the underlying mechanisms which created a diverse life on the earth.
+Estimating shared evolutionary events is an interest of many sub-fields of biology (biogeography etc.,).
+Biogeographers are interested in addressing questions like the number of shared divergence times, the timing of divergence, and whether there is a concordance between geological and biological events across the taxa.
+The usage of phylogenetic models in various fields of biology is wide.
+Therefore, knowing the behavior of models is vital for studies which depend on models to test hypotheses and obtain the results.\\
+In this study, we compared the performance of 3 models (Dirichlet prior, Pitman-Yor prior and Uniform prior) 
+that are implemented in \ecoevolity software which is the primary software we used to estimate the number of shared divergence time among 10 pairs of populations in the past.
+We are interested in how well the models have estimated the shared divergence times and how well the models have estimated which population pairs belong to which divergence time.
+Inferring the shared divergence time across pairs of taxa can reveal the evolutionary history of taxa.
+It also shows what shared mechanism is the driving force for population divergence.
+Temporal patterns
 
-Phylogeographic Study \\
-Sharing divergence time across taxa \\
-Shared divergence across taxa happened via geological events. \\
-Temporal clustering reveals evolutionary history of the taxa. \\
-Temporal pattern- \\
-Model the evolutionary process \\
-Important to know the behavior of the models \\
-Evolutionary events
-
-We compared the performance of 3 models (Dirichlet prior, Pitman-Yor prior and Uniform prior) 
-that are implemented in Ecoevolity software which is the primary software we used to estimate the number of shared divergence time 
-among 10 pairs of populations in the past. We simulated data and know the true number of divergence time from it. We are interested 
-to estimate the number of divergence time from the generated data. We generated data under 5 various ways to putting prior over all
-of the ways that we can assign a pair to divergence event. And then we analyzed the data under 3 models that we can model  
-and have some sense of comparison. We are interested in how well the models have estimated the divergence time and how well 
-the models have estimated what population pairs belong to which divergence time. We assigned prior probabilities to 3 models; how probable each model is. Dirichlet-process prior 
+We assigned prior probabilities to 3 models; how probable each model is. Dirichlet-process prior 
 assigns prior to a new category with probability of \(\dfrac{1}{\concentration +1}\) and an existing category with probability of \(\dfrac{\concentration}{\concentration+1}\).
@@
 
-We used these 3 config files and then added 2 more configs (independent and simutanous configs) to simulate data sets. Independent config 
-basically specifies 10 divergence times and each population diverged independently. Simutanous config specifies that the populations 
-diverged simutanously and there is 1 shared event. And there is another config file which ignores the constant sites (characters). A total of 6 config 
+We used these 3 config files and then added 2 more configs (independent and simultaneous configs) to simulate data sets. Independent config 
+basically specifies 10 divergence times and each population diverged independently. Simultaneous config specifies that the populations 
+diverged simultaneously and there is 1 shared event. And there is another config file which ignores the constant sites (characters). A total of 6 config 
 files are specified to simulate the data sets. We used these 6 config files 4 times to generate scripts and then simulated 10 data sets under each of 
@@
 The times of divergence events were exponentially distributed with a mean 0.05
-expected subsitutions per site.
+expected substitutions per site.
 The mutation-scaled effective sizes ($\epopsize\murate$) of the descendant
@@
 estimation we analyzed data with constant sites and without constant sites. First, we are going 
-to look at the results of divegence time estimation with constant sites. The models which generated 
-the data in rows and columns represent the models under which the data is analyzed. The true divergene 
+to look at the results of divergence time estimation with constant sites. The models which generated 
+the data in rows and columns represent the models under which the data is analyzed. The true divergence 
 time is on x-axis and the estimated divergence time is on y-axis. The results of true divergence 
-time versus estimated divengence time show that all the three models (DP, PYP, and SW) performed
-equally well with very similiar coverage around 95\%. Except for independent all others have truths 
-contianed in within that 95\% credible interval. Independent is little lower because it's evolving 
-indepdently and we are not modeling that way. We haven't observed any patterns that differiate
-these 3 models. Root mean square errors are very similiar across all the models as well. 
+time versus estimated divergence time show that all the three models (DP, PYP, and SW) performed
+equally well with very similar coverage around 95\%. Except for independent all others have truths 
+contained in within that 95\% credible interval. Independent is little lower because it's evolving 
+independently and we are not modeling that way. We haven't observed any patterns that differentiate
+these 3 models. Root mean square errors are very similar across all the models as well. 
 With variable sites only there are more variation in estimates when throwing the invariable 
-sites which contain lot of information and when we use them we have much more presicion in estimates
-than ingoring them. All 10 pairs diverge spontatnous recently causing some MCMC issues and there 
-are very few variable sites all 10 pairs diverged recently. Basicailly there is discrepency bewtween 
+sites which contain lot of information and when we use them we have much more precision in estimates
+than ignoring them. All 10 pairs diverge spontaneous recently causing some MCMC issues and there 
+are very few variable sites all 10 pairs diverged recently. Basically there is discrepancy between 
 gene divergence and population divergence which is the largest at the most recent divergent times.
@@
 which is the correct answer is much lower. But the coverage is unaffected because the 
-likelihood for the missing invariable characters is corrected in \Ecoevolity. PYP is doing better when 
+likelihood for the missing invariable characters is corrected in \ecoevolity. PYP is doing better when 
 dealing with the most difficult scenario all the 10 pairs are diverging independently as well. Both in

### 2023-11-17 manuscript/ms.tex
Starting to work on this ms again.
Making pass over methods section.

@@
 \citet{Oaks2018ecoevolity} and \citet{Oaks2019codemog} for a full description.
-Our model allows for an arbitrary number of two types of temporal comparisons:
+Our model allows for an arbitrary number and mix of two types of temporal
+comparisons:
 \begin{enumerate}
@@
 We assume these characters evolved along their gene trees according to a
-finite-sites continuous-time Markov chain model (CTMC).
+finite-sites continuous-time Markov chain (CTMC) model.
 The equilibrium frequency (\gfreq) of the two character states can be
@@
 Alternatively, if the state frequencies are constrained to be equal, the CTMC
-model is a two-state analog of the ``JC69'' model of nucleotide substitution
+model is a two-state analog of the ``Jukes-Cantor'' model of nucleotide substitution
 \citep{JC1969}.
@@
 distributed according to a parametric continuous probability distribution, like
-a gamma.
+a gamma distribution.
 
@@
 We also implemented what we are calling a ``weighted-uniform'' (\wunif) model
-that has a single ``split weight'' parameter that controls the relative
-probability of models with different numbers of events.
+that has a single ``split weight'' parameter, denoted as \splitweight, that
+controls the relative probability of models with different numbers of events.
 For a given model with \nevents divergence events, the relative probability
@@
 We use Markov chain Monte Carlo (MCMC) algorithms to sample from the joint
-posterior distribution of the divergence model (\etimesets), divergence times
+posterior distribution of divergence models (\etimesets), divergence times
 (\etimes), effective population sizes (\epopsize), and any mutation rate
@@
 This allows us to use the Gibbs sampling algorithm (Algorithm 8) of
-\citet{Neal2000} to update the \etimesets during the MCMC chain.
+\citet{Neal2000} to update \etimesets during the MCMC chain.
 
 Unlike the PYP and DP, where divergence events with the same
-integer partition were equally probably, under the
+integer partition are equally probable, under the
 \wunif prior, divergence events that share the same number of events (\nevents) are
@@
 prior.
-Instead we use reversible-jump MCMC moves under the \wunif prior.
+Instead we use reversible-jump MCMC moves under the \wunif prior \citep{Green1995}.
 
-\subsubsection{reversible-jump MCMC}
-Layout the rjMCMC moves here \ldots
+% \subsubsection{reversible-jump MCMC}
+% Layout the rjMCMC moves here \ldots
 
@@
 
-The models outlined above are implemented in the open-source \cpp package,
+We implemented the models outlined above in the open-source \cpp package,
 \ecoevolity, which is freely available from
@@
 \url{http://phyletica.org/ecoevolity/}.
-The test suite of \ecoevolity
-validates the likelihood calculations and that the MCMC algorithms sample from
-the expected prior distribution when data are ignored.
+In the test suite of \ecoevolity, we validate model likelihood calculations and
+test that the MCMC algorithms sample from the expected prior distribution when
+data are ignored.
 All of our analyses were performed with
@@
 and all of the functionality included in this commit is part of
-the release of Version \highLight{X.X.X}.
+the release of Version \highLight{1.0.0}.
 A detailed history of this project, including all of the scripts
@@
 package
-\citep[Version 0.3.2 Commit c1685dfa][]{Oaks2018ecoevolity}
+\citep[Commit c1685dfa][]{Oaks2018ecoevolity}
 to simulate and analyze \datasets, respectively.
@@
 continuous parameters and the log likelihood using
-\pycoevolity (Version 0.2.6 Commit 27cb15e5).
+\pycoevolity (Commit 27cb15e5).
 When plotting results, we highlight any simulation replicates that have a
@@
 
-In addition to partition distances as metric for \etimesets error, we used
+In addition to partition distance as a metric for \etimesets error, we used
 three additional statistics to quantify performance in estimating \etimesets:
@@
 However, the differences in performance are small and the order of the three
-models mirror the prior probability they place on the independent-divergences
-model.
+models mirror the small differences in prior probability they place on the
+independent-divergences model.
 

### 2025-01-17 images/from-project-repo/copy-plots-from-project-repo.sh
Updating script for pulling pllots from project repo.

@@ -10,5 +10,14 @@ do
         continue
     fi
     project_plot_path="../../../ecoevolity-model-prior/results/plots/${plot_file}"
-    cp "$project_plot_path" "$plot_file"
+    project_gekko_plot_path="../../../ecoevolity-model-prior/results/gekkonid-plots/tex-plot-grids/${plot_file}"
+    if [[ -e "$project_plot_path" ]]
+    then
+        cp "$project_plot_path" "$plot_file"
+    elif [[ -e "$project_gekko_plot_path" ]]
+    then
+        cp "$project_gekko_plot_path" "$plot_file"
+    else
+        echo "WARNING: Could not find path to \"$plot_file\" in project repo"
+    fi
 done

### 2025-01-17 manuscript/ms.tex
Working on manuscript.
Adding figure of Cyrtodactylus results.

Adding Easley cluster to acknowledgements.

Adding citation for pycoevolity.

@@
 continuous parameters and the log likelihood using
-\pycoevolity (Commit 27cb15e5).
+\pycoevolity \citep[Commit 27cb15e5;][]{Oaks2018ecoevolity}.
 When plotting results, we highlight any simulation replicates that have a
@@
 
-\subsection{Empirical application?}
+\subsection{Empirical application}
+
+\begin{figure}[htbp]
+    \begin{center}
+        \includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{../images/from-project-repo/grid-cyrtodactylus-cropped.pdf}
+        \captionsetup{listformat=figList}
+        \caption{
+            Results from the eight pairs of \spp{Cyrtodactylus} populations are
+            robust across all three priors on the clustering of divergence
+            times.
+            We generated the plots using Version 0.2.12 (Commit 06f8bb8) of
+            \pycoevolity \citep{Oaks2018ecoevolity} and Version 3.1.3 of
+            matplotlib \citep{matplotlib}.
+        }
+        \label{fig:cyrtresults}
+    \end{center}
+\end{figure}
 
@@
 The computational work was made possible by the Auburn University (AU) Hopper
-Cluster supported by the AU Office of Information Technology
-and
+and Easley Clusters supported by the AU Office of Information Technology and
 a grant of high-performance computing resources and technical support from the
